### 2019-05-11 papers/haskell19/8-conclusions.tex
NIT

In the future, we aim to minimize the runtime overhead of our technique, using
perhaps prefix-free encodings based on generation frequencies, as a way to
reduce the representation bureaucracy as much as possible.
%
In addition, using type-level representations for each random construction
leaves the door open for extending our approach with a composable mechanism for
predicting the distributions of random values.
%
This would be possible by overloading each representation type with stochastic
information describing its branching behavior---interesting thoughts to motivate
our future research.

>>>>

In the future, we aim to minimize the runtime overhead of our technique, using
perhaps prefix-free encodings based on generation frequencies, as a way to
reduce the representation bureaucracy as much as possible.
%
In addition, by using type-level representations for each random construction,
we leave the door open to extend our approach with a composable mechanism to
predict and optimize the distributions of random values.
%
This would be possible by overloading each representation type with stochastic
information describing its branching behavior---interesting thoughts to motivate
our future research.
